A Domain Specific Language for SpectreGuard

### 2020-12-06 paper/main.tex
an inference reference; change size of syntax table

\lstset{breaklines=true, basicstyle=\ttfamily\tiny, escapeinside={(*@}{@*)}}

@@

\setlength\extrarowheight{1.5pt}

@@

  A Spectre mitigation strategy in the form of a mechanism for marking variables as "non-speculative" was developed in
  \cite{SpectreGuard}. In this paper, we develop an embedded domain specific language (EDSL) in Haskell to provide
  support for this feature. The static type system of Haskell is used so that many basic forms of copying
  secret variables to public variables are disallowed. Additionally, a static analysis was developed which
  will detect some cases of secret variables leaking to public variables via control flow constructs.

@@

@@

\section{Sensitivity Types}
The Haskell type system is leveraged to perform a basic static consistency check of the sensitivities
of variables, so that a variable does not get assigned to a variable of a different sensitivity. The
logical inference rules corresponding to this check are given in Fig. \ref{fig:SensTypes}.

@@

where \ttt{x} is some expression or command in the EDSL. This judgment means
that \ttt{x} has type $\beta$. This is the same syntax used by Haskell, and by extension
the EDSL, to explicitly specify a type in an expression.

@@

Additionally, features to safely convert between sensitivity levels could prove
useful. A conversion from public to secret would be straightforward. A conversion
going the other direction could be provided by an instruction in the EDSL
which might perform a mitigation measure, such as a cache flush. \cite{PLtea-james}

>>>>

\lstset{breaklines=true, basicstyle=\ttfamily\fontsize{6}{7}\selectfont, escapeinside={(*@}{@*)}}

@@

\setlength\extrarowheight{1.5pt}
\setlength{\tabcolsep}{1pt}

@@

  A Spectre mitigation strategy in the form of a mechanism for marking variables
  as "non-speculative" was developed in \cite{SpectreGuard}. In this paper, we
  develop an embedded domain specific language (EDSL) in Haskell to provide
  support for this feature, with a backend that generates C code. The static
  type system of Haskell is used so that many basic forms of copying secret
  variables to public variables are disallowed. Additionally, a static analysis
  was developed which will detect some cases of secret variables leaking to
  public variables via control flow constructs.

@@

This also outlines procedure that the C code generator uses.

@@

\section{Sensitivity Types}
The Haskell type system is leveraged to perform a basic static consistency check of the sensitivities
of variables, so that a variable does not get assigned to a variable of a different sensitivity. The
logical inference rules corresponding to this check are given in Fig. \ref{fig:SensTypes}. An introduction
to this style of inference rule system, with many examples and applications in the study of programming languages, is given in \cite{HarperFoundations}.

@@

where \ttt{x} is some expression or command in the EDSL. This judgement means
that \ttt{x} has type $\beta$. This is also the same syntax used by Haskell, and by extension
the EDSL, to explicitly specify the type of any expression when necessary or desired.

@@

Additionally, features to safely convert between sensitivity levels could prove
useful. A conversion from public to secret would be straightforward. A situational conversion
going the other direction could be provided by an instruction in the EDSL
which might perform a Spectre mitigation measure, such as a cache flush. \cite{PLtea-james}
